---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nowaste)
```

```{r}
plot_plastic_density(plastic_data, variable = "plastic_per_capita")
```

This function creates a density plot showing the distribution of plastic waste per capita across countries.


```{r}
table_waste_by_income(joined_all) #need other data
```

This function groups countries into GDP per capita income categories and creates a formatted table summarizing the number of countries, average GDP per capita, average plastic waste per person, median plastic waste per person, and total recorded plastic waste.


```{r}
plot_gdp_vs_plastic(joined_all) #need other data
```

This function creates a scatterplot comparing GDP per capita and total recorded plastic waste by country. Countries are colored by world region.


